business-attributes

### 2016-08-05 eda/business-attributes.Rmd
updated business attributes

```{r}
us_business <- read_csv('us-business.csv')
noise_level <- read_csv('noise-attr.csv') 
attire_type <- read_csv('attire-attr.csv')

states <- map_data('state')
ggplot(states) + 
  geom_polygon(aes(x = long, 
                   y = lat, 
                   group = group), 
               fill = "grey80", 
               color = "white") + 
  coord_fixed(1.3) + 
  geom_point(data = us_business, 
             aes(long, 
                 lat, 
                 color = factor(stars), 
                 size = count), 
             alpha = 0.7) + 
  guides(colour = guide_legend("Star Rating"), 
         size = guide_legend("Review Counts")) + 
  labs(title = "Restaurant Reviews in United States") +
  theme_nothing(legend = TRUE)
```

## Exploring Noise Level

As expected, restaurants with many reviews and/or high ratings were clustered in specific regions. This table shows where most restaurants are clustered around. I have chosen 4 regions with most businesses: Nevada, Arizona, North Carolina and Pennsylvania.

```{r}
top_data <- us_business %>% 
  group_by(state) %>% 
  tally()
top_data
```

There were many attributes per restaurant, and some were more influential directly/indirectly to a business' success. I have first decided to see how noise level would influcence the star ratings of customers. 
I grouped the data frame by 'state' and 'noise' and created a new column having the average star rating per group. The plot didn't know which noise level to plot first, so I have created the factor levels in noise level.

```{r}
ggplot(data=noise_level, aes(x = noise_factored,
                            y = star, 
                            fill = state)) +
  geom_bar(stat = "identity", 
           position = "dodge") +
  scale_x_discrete(labels = c("Quiet", "Average", "Loud", "Very Loud")) +
  labs(title = "How Noise Level Influences Average Star Ratings") + 
  xlab("Noise Level") + 
  ylab("Average Star Ratings") +
  guides(fill = guide_legend("Region"))
```

## Exploring Attire Types
Now to another business attribute: attire. Similar to noise data, attire_data was retrived by grouping the data frame by 'state' and 'attire'. Again, the star ratings were the means of each group's star ratings.

```{r}
ggplot(data=attire_type, aes(x=attire, y=star, fill=state)) +
  geom_bar(stat="identity", position = "dodge") +
  labs(title = "How Attire Influences Average Star Ratings") + 
  xlab("Attire") + 
  ylab("Average Star Ratings") + 
  guides(fill = guide_legend("Region"))
```

>>>>

There were only six states that have businesses reviewed more than 300 times.

```{r}
business <- read_csv("../clean_data/yelp_business.csv")
```

```{r}
successful_business <- business %>% 
  select(-open) %>% 
  filter(review_count > 300) %>% 
  group_by(state) %>% 
  summarise(num = n())

names(business) <- c("id", "open", "categories", "count", "state", "stars", "noise", "attire", "Take-out", "Takes Reservation", "Offers Delivery", "Outdoor Seating", "Accepts Credit Card", "Happy Hour")

ggplot(successful_business, aes(x = reorder(state, -num), 
                                y= num)) + 
  geom_bar(stat = "identity", 
           position = "dodge") +
  labs(title = "Number of Businesses with more than 300 Reviews") + 
  xlab("State") + 
  ylab("Number of Businesses") 
```

## Exploring Attributes

As expected, restaurants with many reviews and/or high ratings were clustered in specific regions.

```{r}
business_attributes <- business %>% 
  filter(count > 300) %>% 
  select(-open, -count, -categories, -noise, -attire) %>% 
  gather(key=Attribute, value=Val, -id, -state, -stars) %>% 
  na.omit
```

There were many attributes per restaurant, and some of them were believed to be influential to a business' success. I have first chosen six main attributes that seemed critical to the customers' star ratings.

I gathered all the attributes and used facet_wrap to plot six seperate graphs. The left chunk represents True and the right represents False. There are some states where there's no applicable values for the specific attribute.

```{r}
ggplot(business_attributes, 
       aes(x = factor(Val, 
                      levels = c("TRUE","FALSE")), 
           y = stars, 
           fill = state)) + 
  facet_wrap(~Attribute) + 
  geom_bar(stat = "identity",
           position = "dodge") +
  labs(title = "User Ratings on Business Attributes") +
  xlab("") + 
  ylab("Star Rating") +
  scale_fill_discrete(name = "State")
```
